

%----------------------------------------------------------------------------------------
%	ADDRESSEE SECTION
%----------------------------------------------------------------------------------------
\documentclass[10pt]{letter} % 10pt font size default, 11pt and 12pt are also possible

\usepackage{geometry} % Required for adjusting page dimensions

%\longindentation=0pt % Un-commenting this line will push the closing "Sincerely," to the left of the page

\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	top=2cm, % Top margin
	bottom=1.5cm, % Bottom margin
	left=2.5cm, % Left margin
	right=2.5cm, % Right margin
	%showframe, % Uncomment to show how the type block is set on the page
}

\usepackage[T1]{fontenc} % Output font encoding for international characters
\usepackage[utf8]{inputenc} % Required for inputting international characters
\usepackage{color}
\usepackage{stix} % Use the Stix font by default

\usepackage{microtype} % Improve justification
\usepackage{dashrule}

%----------------------------------------------------------------------------------------
%	YOUR NAME & ADDRESS SECTION
%----------------------------------------------------------------------------------------

%\signature{John Smith} % Your name for the signature at the bottom

%\address{123 Broadway \\ City, State 12345 \\ (000) 111-1111} % Your address and phone number

%----------------------------------------------------------------------------------------
\newcommand{\mdf}[1]{\textcolor[rgb]{1.00,0.00,1.00}{#1}}
\begin{document}
	\textbf{Dear Editor,}\\
	Thank you for handling our manuscript. Our submission paper1027 entitled ``Preventing Self-intersection with Cycle Regularization in Mesh
	Reconstruction Networks'' was reviewed in GMP2019 and recommended to your journal for a fast-track submission process. The reviewers’ comments to be very valuable and helpful in improving our presentation, as well as important for guiding significantly to our research. We have read the comments carefully and revised our manuscript according to these comments and suggestions. All the modifications are \mdf{highlighted in magenta} in the revised manuscript by the macro $\backslash$mdf in the source file. Listed below are our point-by-point responses to the reviewer comments.\\
	
	\hdashrule{\linewidth}{1pt}{1mm}
	Chair:
	
	[Q]: \emph{The revision should focus on the case of models of non-zero genus.}
	
	[A]: As a response to chair's directives, we have added extra experiments in our revised paper to test our proposed cycle regularization on cases of genus-one models. The experimental results are shown in Figure 6. We also add discussion about these results at Sec 4.1 from Line 267 as follows:
	 
	\mdf{We also explore into cases with higher genus by manually choosing torus as the source surface. Though this is not a viable approach to enable neural networks to generate shapes with complex topology, it allows us to observe the effect of our cycle regularization in the cases of genus-one. As shown in Figure 6, with a torus as the source surface, the cycle regularization significantly reduces self-intersection and prevents the collapse of the hole in the torus. As shown in the cases of ``okay" and ``love" shapes, the outputs without cycle regularization are wildly self-intersected and the hole in the toruses both collapsed, while the outputs with cycle regularization all preserve the hole. However, the torus-based outputs are more easily to get stuck at a local minimum of the cycle regularization term where the remaining self-intersected triangles tends to twist together and form two knots. With a spherical source surface, though the outputs do not contain the hole as in the ground truth models, they are less likely to get stuck at a local minimum of the cycle regularization term with self-intersections.
	}
	
	\hdashrule{\linewidth}{1pt}{1mm}
	%----------------------------------------------------------------------------------------
	Reviewer 21833:
	
	[Q]: \emph{I recommend to state the 2D image input directly in the title.}
	
	[A]: We have changed our title to ``Preventing Self-intersection with Cycle Regularization \mdf{in Neural Networks for Mesh Reconstruction from a Single RGB Image}''.
	
	[Q]: \emph{The paper should also better distinguish between local and global self-intersections. The non-vanishing Jacobian guarantees self-intersection free mapping only locally, which is probably the main objective of the current work, but global interference should be briefly discussed too.}
	
	[A]: To clarify that non-vanishing Jacobian only prevents self-intersection locally, we have rewritten our discussion about existing strategy for enforcing injectivity in the Introduction Section from Line 44 as follows:
	
	\mdf{To enforce injectivity, one possible strategy is to start from a feasible solution and keep every deformation or optimization step inside feasible regions. In works of deformation (e.g. Sederberg and Parry (1986); Gain and Dodgson (2001)), such strategy is usually excuted as follows. A clean mesh that is free from self-intersection is chosen as the initial mesh and local self-intersection is prevented by constraining the Jacobian of the mapping function in the subsequent steps in deformation. In works of parameterization optimization for surface with disk topology, Tutte’s embedding Tutte (1963) or its variants are typically employed to get an initial bijective mapping and triangle fold (local self-intersection) is prevented with different techniques in following optimization steps. More specifically, triangle fold can be prevented by adding barrier energy from distortion metrics (e.g. Poranne and Lipman (2014); Aigerman et al. (2014)), bounding the triangle distortion (e.g. Smith and Schaefer (2015); Lipman (2012)) or using a progressive strategy Liu et al. (2018).}
	
	To emphasize that our technique reduces both local and global self-intersections, we also add statement in the Introduction Section from line 60 as follows:
	
	In order to learn injective mapping for meshes, \mdf{we propose cycle regularization which is deduced from the basic decision theorem of injectivity. It reduces not only local self-intersections but also global self-interferences of the surface.}
	
	[Q]: 
	\emph{There are several relevant references that deal with local self-intersection free mappings, see e.g.:\\
	Sederberg, T.W. and Parry, S.R., 1986. Free-form deformation of solid geometric models. ACM SIGGRAPH computer graphics, 20(4), pp.151-160.\\
	Schüller, C., Kavan, L., Panozzo, D. and Sorkine-Hornung, O., 2013, July. Locally injective mappings. In Proceedings of the Eleventh Eurographics/ACMSIGGRAPH Symposium on Geometry Processing (pp. 125-135). Eurographics Association.\\
	Pekerman, D., Elber, G. and Kim, M.S., 2008. Self-intersection detection and elimination in freeform curves and surfaces. Computer-Aided Design, 40(2), pp.150-159.}

	[A]: We have added these references and discussed them in Introduction and Related Work sections.
	
	[Q]: \emph{The structure of the paper is quite unfortunate. For example Section 3.1. refers to Definition 1 that appears later; this is very reader-unfriendly.}
	
	[A]: We have adjusted our manuscript to avoid such case as much as we can. Now the Definition 1 appears before it is referred to at Line 153.
	
	[Q]: \emph{Moreover, the paper speaks about injectivity of $f$ and self-overlapped points like these were two different phenomena.}
	
	[A]: Injectivity is a property of the regressed function $f$. Self-overlapped 3D points are observed defects on surface meshes. They are naturally related but we want to explain the underlying relationship between these two concepts clearly by elaborating them separately.
	
	[Q]: \emph{Another rather confusing part is Def. 1 itself. Why do you formulate (1) and (2)? These are obviously equivalent and there is no reason to state them both.}
	
	[A]: Yes, the two formulations are equivalent, which is why we use ``Equivalently'' in Def. 1. However, we keep these two formulations in order to express the injectivity property in different ways. Eq.(1) states that each element in the function's co-domain must come from at most one element in domain. Eq.(2) states that an injective function never maps different points to same position. Eq.(1) is more commonly seen in text books while Eq.(2) explains why injectivity means no self-overlapped points in a more straightforward manner. Though it is somewhat redundant, we keep both formulation Eq.(1) and Eq.(2) to make our idea clear for audience from different backgrounds.
	
	[Q]: \emph{Fig.8 is very small and the zoom-in is barely visible.  Some other figures should be provided in higher resolution, e.g. the *Input* row in Fig.6 is really bad.} 
	
	[A]: We use the images in the benchmark dataset without any modification. The original size of the images are $224 \times 224$, which is currently a common setting for the techniques with neural networks. We have enlarged the images for output shapes in the original Figure 8 as Figure 9 in our revised manuscript.
	
	[Q]: \emph{Looking at fig. 4, One wonders how many iterations are needed to receive results with desired chamfer distance. How do you set the number of iterations in your algorithm; what is the termination criterion?}
	
	[A]: We plot the loss curve to show the convergence in Figure 4 and add explanation at Sec. 4.1 from Line 254 as follows:
	
	\mdf{We set the maximum iteration number to 1024 for all experiments in this subsection. As shown in Figure 4, the optimization process typically converges much earlier before 1024 iterations.}
	
	[Q]: \emph{What about objects with other genus than zero?}
	
	[A]: As our response to the Chair's directives, we tested the proposed cycle regularization on some genus-one cases by manually choosing torus as the source surface. In such cases, we discover that though the proposed cycle regularization still significantly reduces self-intersections, it is more likely to get stuck at a local minimum with remaining self-intersected triangles than using spherical source surface.   
	 
	\hdashrule{\linewidth}{1pt}{1mm}
	%----------------------------------------------------------------------------------------
	Reviewer 21924:
	
	Thank you for your endorsement of our work.
	
	[Q]: \emph{there are approaches addressing intersections introduced in recent years, although not learning based approaches, such as:
	"Yixin Hu, Qingnan Zhou, Xifeng Gao, Alec Jacobson, Denis Zorin, Daniele Panozzo. ACM Transactions on Graphics (SIGGRAPH 2018)"
	"Yijing Li, Jernej Barbi?: Immersion of Self-Intersecting Solids and Surfaces, ACM Transactions on Graphics 37(4) (SIGGRAPH 2018), Aug 2018"}
	
	[A]: We have added Li et al. (2018) in our related work in Sec. 2.5 Line 143 as one of the non-learning based methods. Hu et al. (2018) focus on tetrahedral meshing and is less related to the subject of our paper.
	
	[Q]: The drawback is that it penalizes the appearance of intersections, but doesn't completely eliminate the issue.
	
	[A]: Yes. Thanks for pointing it out. In the proposed technique, injectivity is formulated as a regularization term so that it is easily integrated into current neural networks. For now, we do not have a practical solution to integrate injectivity as a  hard constraint into neural networks to to guarantee no self-intersections. We discuss this issue in Sec. 4.3 and will study it in our future work. 
	
	\hdashrule{\linewidth}{1pt}{1mm}
	%----------------------------------------------------------------------------------------
	Reviewer 21930:
	
	Thank you for your approval on our work and advices of making our draft better.
	
	[Q]: \emph{In Proposition 1, the free variable x should be bound by a quantifier.
		\\The first sentence of section 3.3 is describing a version of the Universal Approximation Theorem and would do well to refer to this.}
	
	[A]: We have fixed these two issues in our revised paper. 
	
	[Q]: \emph{A rather stringent limitation of the method is that it only applies to models with zero genus.}
	
	[A]: As our response to the Chair's directives, we tested the proposed cycle regularization on some genus-one cases. The results show that the cycle regularization will benefit the genus-one cases in reducing self-intersections as well but not as good as it does for the zero genus cases.
\end{document}